\documentclass{cv_style}
\AtEveryBibitem{\clearfield{month}}
\AtEveryBibitem{\clearfield{day}}
\usepackage{enumitem}
\hypersetup{
  colorlinks = true,
  linkcolor = blue,
  urlcolor = blue,
  citecolor = blue
}
\begin{document}
\name{\textbf{Matthew M. Lee, PhD, SM, MS}}
\begin{center}
    \contact{665 Huntington Avenue}{Boston}{MA}{matthewlee@hsph.harvard.edu}{\href{https://mmlee.me}{https://mmlee.me}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{adjustwidth}{0.7cm}{0.7cm} \parskip 8pt \begin{small} \textbf{Summary:} I am a postdoctoral research fellow at the Harvard T.H. Chan School of Public Health in the Department of Social and Behavioral Sciences at the \href{https://www.hsph.harvard.edu/sphere/}{Social Policies for Health Equity Research (SPHERE) Center}, with support from the \href{https://www.hsph.harvard.edu/cvdepi/predocpostdoc-training-program/}{NHLBI CVD Epidemiology Training Program in Behavior, the Environment, and Global Health}. My research spans the intersections of social and food policy interventions and their impacts to nutrition, food insecurity, cardiometabolic disease, and population health. I am particularly interested in applying novel econometric and epidemiologic methods to improve estimation of the causal effects of these programs, and in understanding the role of targeted vs. population-level strategies to improve health equity.  
\end{small}
\end{adjustwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip -5pt 
\section{Education}
\parskip -5pt
% PhD Harvard
\datedsubsection{\textbf{Harvard T.H. Chan School of Public Health}}{May 2024}
\parskip -4pt \noindent Doctor of Philosophy (PhD) in Population Health Science, Public Health Nutrition \\

\vspace{-1em}


% SM Harvard
\datedsubsection{\textbf{Harvard T.H. Chan School of Public Health}}{May 2024}
\parskip -4pt \noindent Master of Science (SM) in Biostatistics

% Berkeley MS
\datedsubsection{\textbf{University of California, Berkeley School of Public Health}}{May 2019}
\parskip -4pt Master of Science (MS) in Epidemiology 

% Berkeley BA
\datedsubsection{\textbf{University of California, Berkeley}}{May 2016}
\parskip -4pt \noindent  Bachelor of Arts (BA) in Public Health, \textsc{Minors:} Global Poverty, Music

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Appointments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip -5pt 
\section{Relevant Research Experience}
\parskip -5pt
% SBS postdoc Harvard
\datedsubsection{\textbf{Postdoctoral Research Fellow}}{August 2024-present}
\parskip -4pt \noindent Harvard T.H. Chan School of Public Health, Department of Social and Behavioral Sciences \\
CVD Epidemiology Training Program in Behavior, the Environment and Global Health 

\vspace{1em}

\textit{\textbf{Current projects related to social policy:}}
\begin{itemize}
    \item Testing the impact of county-level economic, containment, and public health policies that were implemented during the COVID-19 pandemic and their disparate impacts on child food insecurity and BMI, using restricted-use data from the National Health Interview Survey. \parskip 1pt
    \item Understanding the comparative effectiveness of randomly-allocated texting-based vs. personal support interventions to increase take-up of the Earned Income Tax Credit among Californians participating in the Special Supplemental Nutrition Assistance Program for Women, Infants, and Children. \parskip 1pt
    \item Assessing the heterogeneous impacts of state paid family leave policies and breastfeeding initiation using data from the Pregnancy Risk Assessment Monitoring System. \parskip 1pt
    \item Comparing differences in diet following provision of unconditional cash transfers during the COVID-19 pandemic in Chelsea, Massachusetts: A randomized lottery experiment.
\end{itemize}

\vspace{1em}
\textit{\textbf{Current projects related to food policy:}}
\begin{itemize}
    \item Examining the relationship between changes to the WIC program during COVID-19, including increases to the monthly cash value voucher allocation for fresh fruits and vegetables, on retention and benefit redemption, using Massachusetts state-wide administrative data. \parskip 1pt
    \item Understanding the impact of COVID-19 changes to WIC and SNAP on experiences of participation, a qualitative study of co-participants of both programs. \parskip 1pt
    \item Estimating associations between changes in adherence to US dietary guidelines and BMI among adolescents in the Growing Up Today Study: A prospective cohort study.
\end{itemize}

% Kenney
\datedsubsection{\textbf{Researcher in Nutrition}}{Jan 2020-May 2024}
\textit{Harvard T.H. Chan School of Public Health} \\
PI: Erica Kenney, ScD, MPH
\begin{itemize}
    \item Led and supported data analysis, code review, and manuscript development and editing for projects related to nutrition policies aimed at addressing childhood obesity, improving food access, and reducing food insecurity -- including evaluations of US nutrition assistance programs, of the Philadelphia, PA, sweetened beverage excise tax, of racial/ethnic disparities in food-related advertising to young children and their families, and of WIC benefits expansions during the COVID-19 pandemic.
\end{itemize}

% CHOICES
\datedsubsection{\textbf{Researcher in Social and Behavioral Sciences}}{Jan 2020-May 2024}
\textit{Harvard T.H. Chan School of Public Health} \\
PI: Steve Gortmaker, PhD, The Childhood Obesity Intervention Cost-Effectiveness Study (CHOICES)
\begin{itemize}
    \item Supported microsimulation-based cost-effectiveness analyses related to US policy interventions and their potential long-run impacts on child and adult outcomes, including health care spending, obesity, morbidity, and mortality. Analyzed dietary and health data from representative samples including the National Health and Nutrition Examination Survey, ran and synthesized output from simulation models, validated estimates against empirical data, and developed methods to streamline post-processing of results.
\end{itemize}

% UCB Madsen
\datedsubsection{\textbf{Researcher in Community Health Sciences}}{Aug 2017-May 2019}
\textit{UC Berkeley School of Public Health} \\
PI: Kristine Madsen, MD, MPH
\begin{itemize}
    \item Managed evaluation of sugar-sweetened beverage (SSB) taxes in Oakland, Berkeley, and San Francisco to assess the relationship between implementation and beverage consumption, using a quasi-experimental difference-in-differences design. Supported analysis for \textit{The Fit Study}, a three year cluster-randomized trial on the effects of BMI screening and reporting. Oversaw data collection, entry, analysis, and manuscript development and submission.
    \item \parskip 1pt Produced spatial data cross-linked with information from the California Department of Education, American Community Survey, and US Census for projects examining the role of targeted marketing of SSBs and the spillover effects of Physical Education related lawsuits on district PE policies in California.
\end{itemize}

% UCB Mujahid/Bradshaw
\datedsubsection{\textbf{Staff Research Associate}}{June 2016-Aug 2017}
\textit{UC Berkeley School of Public Health Division of Epidemiology} \\
PI: Mahasin Mujahid, PhD, MS; Patrick Bradshaw, PhD, MS
\begin{itemize}
    \item Managed research portfolio, including background literature reviews, Institutional Review Board (IRB) and ethics approval and documentation, accounting and finance reporting, data management, manuscript preparation and submission, and grant proposals. Provided teaching support for undergraduate-level Epidemiologic Methods course.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parskip -5pt 
\nocite{*}
\printbibliography[title=Publications]

\vspace{2em}

\textit{Ad Hoc Reviewer for: The American Journal of Public Health (AJPH), Journal of the Academy of Nutrition and Dietetics (JAND), PLOS ONE, PLOS Medicine, The American Journal of Preventive Medicine (AJPM) FOCUS, AJPM, Pediatrics, BMC Public Health, Scientific Reports, Frontiers in Nutrition, Preventive Medicine Reports, Public Health, International Journal of Obesity, Journal of Nutritional Science}


\section{Presentations}
\begin{enumerate}[leftmargin = 2em]
    \item \textbf{Lee MM}, Poole MK, Chen JT, Gortmaker SL, Stephenson BK, Haines J, Chavarro J, Kenney EL.  Longitudinal Changes in Adherence to US Dietary Guidelines and Associations With Body Mass Index Among Adolescents in the Growing Up Today Study: A Change-in-Change Study.  \textit{American Society of Nutrition Annual Meeting}. (July 2024). 
    \item \parskip 1pt Chapman LE, Richardson SA, Rimm EB, Gortmaker SL, \textbf{Lee MM}, Cohen JFW. Examining Student Plate Waste Following a Conversion From Pre-packaged to Scratch-Cooked Lunches Prepared On-Site: A Longitudinal Cohort Study. \textit{American Society of Nutrition Annual Meeting}. (July 2024). 
    \item \parskip 1pt \textbf{Lee MM}, Kenney EL, Carlson K, Novick E, Portocarrero P, Rimm EB, Chen JT, Gortmaker SL, Stephenson BK, Liebman J. Impact of unconditional cash transfers on diet during the COVID-19 pandemic: A randomized lottery experiment. \textit{American Public Health Association Annual Meeting}. (Nov 2023). 
    \item \parskip 1pt \textbf{Lee MM}, Gibson LA, Hua SV, Lowery CM, Paul M, Roberto CA, Lawman HG, Bleich SN, Mitra N, Kenney EL. Changes in advertising and store stocking practices among small, independent beverage retailers following a sweetened beverage excise tax in Philadelphia: A difference-in-differences study. \textit{American Public Health Association Annual Meeting}. (Nov 2023).  
    \item \parskip 1pt Chapman L, Richardson S, Rimm EB, Gortmaker SL, \textbf{Lee MM}, Cohen J. Daily saturated fat and sodium content of school meals among a nationally representative sample of elementary schools in the United States. \textit{American Public Health Association Annual Meeting}. (Nov 2023). 
    \item \parskip 1pt \textbf{Lee MM}, Barrett J, Kenney EL, Gouck J, Cradock AL, Long MW, Ward ZJ, Rohrer B, Gortmaker SL. Impacts of a state-wide sugar-sweetened beverage excise tax in California: Projected benefits for population obesity and health equity. \textit{American Public Health Association Annual Meeting}. (2022).
    \item \parskip 1pt Kenney EL, \textbf{Lee MM}, Barrett J, Ward ZJ, Long MW, Cradock AL, Gortmaker SL. The cost-effectiveness and health equity impacts of improved nutrition standards in WIC, and the potential for maximizing WIC’s benefits for population health. \textit{American Public Health Association Annual Meeting}. (2022).
    \item \parskip 1pt Yuan H, Schillinger D, Ponce J, \textbf{Lee MM},  Falbe J, Daniels R, Madsen K. Implementation of 3 sugar-sweetened beverage taxes in California Bay Area. \textit{American Public Health Association Annual Meeting}. (2019).
\end{enumerate}

\section{Invited Lectures}
\begin{enumerate}[leftmargin = 2em]
    \item Equitable Food Policy in the United States. California State University, Long Beach. H SC 507: Health Equity and Health Disparities Research in the US. October 2024.
    \item \parskip 1pt Assessing outcome evaluation study designs, quality, and considerations for health equity. NUT 232: Designing and Evaluating Behavioral Interventions Targeting Diet. November 2024.
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Honors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards \& Honors}

\textit{ASN Emerging Leaders in Nutrition Science Award} \hfill {2024}\\
\textit{APHA Annual Conference Food and Nutrition Abstract Award} \hfill {2023}\\
\textit{GSAS Professional Development Fund Recipient} \hfill {2023}\\
\textit{Irene M. \& Fredrick J. Stare Nutrition Education Fund Awardee} \hfill {2022}\\
\textit{Berkowitz Fellowship in Public Health} \hfill {2021}\\
\textit{Certificate of Distinction in Teaching, Derek Bok Center for Teaching and Learning} \hfill {2021}\\
\textit{Certificate of Distinction in Teaching, Derek Bok Center for Teaching and Learning} \hfill {2020}\\
\textit{Simon, Arpi, and Marie Simonian Research Excellence in Nutrition Prize} \hfill {2020} \\
\textit{Prajna Chair's Scholarship in Public Health Nutrition} \hfill 2019 \\
\textit{Reshetko Family Scholarship} \hfill 2017



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEACHING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip -5pt 
\section{Teaching and Mentoring}

% PHS 2000A/B
\datedsubsection{\textbf{Teaching Fellow, Population Health Sciences 2000 A/B}}{2020-2021, 2022}
``Quantitative Research Methods in Population Health Sciences'' | \textit{Harvard GSAS}
\begin{itemize}
  \vspace{0em} \item Year-long core course for first-year PhD students in the Population Health Sciences doctoral program, covering concepts in sampling, estimation and statistical inference for regression models, model selection, survival and longitudinal analyses, measurement error, causal inference and mediation, and econometrics. 
  \item \parskip 1pt Led lab sessions and weekly office hours with original lecture slides including applications using the R programming language, development and grading of homework and exam assessments, and primary role in course evaluation and refinement during transition to online/virtual learning. Lab lectures given included material on regression, measurement error, survival analysis, causal interaction and mediation, factor analysis, and meta-analysis.
\end{itemize}

% SBS 203/204
\datedsubsection{\textbf{Teaching Fellow, Social and Behavioral Sciences 203/204}}{2022, 2023, 2024}
``Program Implementation and Evaluation'' | \textit{Harvard T.H. Chan School of Public Health}
\begin{itemize}
  \vspace{0em} \item Semester course on conducting community health needs assessment, program planning, implementation, and evaluation, with a particular emphasis on community engagement and applied research. Required for masters students in Social and Behavioral Sciences. Foci includes health-related intervention for individuals, communities, organizations, and local/national groups and the various challenges that researchers and practitioners encounter when conducting this work "on the ground". 
  \item \parskip 1pt Facilitated in-class discussion on theoretical concepts and course materials, led lecture in cost effectiveness analysis and economic evaluation in the context of program planning, and provided critical feedback on student work, including a community health needs assessment and CDC \textit{Partnerships for Improving Community Health} grant application among others. 
\end{itemize}

% NUT 202
\datedsubsection{\textbf{Teaching Fellow, Nutrition 202}}{2022}
``The Biological Basis of Human Nutrition'' | \textit{Harvard T.H. Chan School of Public Health}
\begin{itemize}
  \vspace{0em} \item Semester course on the biochemistry and metabolism of carbohydrates, fats, proteins, vitamins, and minerals in the context of human disease. Contemporary topics are emphasized. Particular emphasis is given to current knowledge of the mechanisms that may explain the role of diet in the causation and/or prevention of ischemic heart disease, diabetes, obesity, hypertension, and cancer. Required for masters and doctoral students in Nutrition.
  \item \parskip 1pt Coordinated weekly guest lectures and held weekly office hour review sessions on course material, led lecture in iron and copper metabolism in the context of human nutrition and health, drafted and evaluated exam questions and facilitated course feedback.
\end{itemize}

% PHS 2000A/B Tutor
\datedsubsection{\textbf{Tutor, Population Health Sciences 2000 A/B}}{2021-22}
``Quantitative Research Methods in Population Health Sciences'' | \textit{Harvard GSAS}
\begin{itemize}
  \vspace{0em} \item Hosted weekly tutoring sessions for 2-3 first-year PhD students in Population Health Sciences to support learning in PHS 2000A and B (course description above), review concepts in preparation for exams, go over solutions and concepts from problem sets, and provide mentoring on additional classes and resources.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Service}

% Union
\datedsubsection{\textbf{Union Steward}}{2020-2021}
\textit{Harvard Graduate Student Union}
\begin{itemize}
    \item Supported department- and university-level organizing efforts to assess student needs, gauge contract priorities, and build social support amongst incoming and continuing doctoral students in the School of Public Health. 
\end{itemize}

% Suitcase Clinic
\datedsubsection{\textbf{Executive Director / Housing and Employment Coordinator}}{2013-2015}
\textit{The Suitcase Clinic}
\begin{itemize}
    \item Oversaw all volunteers, committees, and clinics aimed at providing health and social services to homeless and low-income populations in the Bay Area, including a course on issues on homelessness for UC Berkeley  students. 
    \item \parskip 1pt Built and maintained relationships with partners including The City of Berkeley and Berkeley Free Clinic, worked effectively to secure \$40,000 in funding, and initiated process for attaining 501(c)3 status. Initiated data collection and electronic services database to bolster institutional memory, and created stable budget and accounting process.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\begin{itemize}
    \item Programming languages: 
    \begin{itemize}
        \item Statistical analysis (R, Stata, SAS, Python, Stan)
        \item \parskip 1pt Geographic Information Systems (R)
        \item \parskip 1pt Typesetting (\LaTeX, R Markdown, R Sweave, Markdown) 
        \item \parskip 1pt Presentations (react.js, R) 
    \end{itemize}
    \item \parskip 1pt High performance computing cluster-based analysis
    \item \parskip 1pt Other software: 
    \begin{itemize}
        \item \parskip 1pt Qualitative analysis (Atlas.ti, Dedoose)
        \item \parskip 1pt Reference Management (Endnote, Refworks, Zotero, Mendeley)
        \item \parskip 1pt Microsoft Office/Google Suite (Microsoft Word, PowerPoint, Excel; Google Docs, Sheets, Slides)
        \item \parskip 1pt Adobe Creative Suite (Photoshop, Illustrator, InDesign, Premiere, Lightroom, Bridge)
    \end{itemize}
    \item \parskip 1pt Version control (Git/GitHub)
    \item \parskip 1pt Survey design (Qualtrics, Google Forms)
\end{itemize}

\end{document}