\documentclass{cv_style}
\AtEveryBibitem{\clearfield{month}}
\AtEveryBibitem{\clearfield{day}}
\usepackage{enumitem}
\hypersetup{
  colorlinks = true,
  linkcolor = blue,
  urlcolor = blue,
  citecolor = blue
}
\begin{document}
\name{\textbf{Matthew M. Lee, PhD, SM, MS}}
\begin{center}
    \contact{677 Huntington Ave}{Boston}{MA}{mlee26@gmail.com}{Day/Evening Phone: (916) 642-3497}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{adjustwidth}{0.7cm}{0.7cm} \parskip 8pt \begin{small} \textbf{Summary:} I am a postdoctoral research fellow at the Harvard T.H. Chan School of Public Health in the Department of Social and Behavioral Sciences. My professional interests are focused on policies and interventions related to food systems and the environment that improve cardiometabolic outcomes, as well as the application of novel causal inference and simulation-based methods to advance population health and health equity research.  
\end{small}
\end{adjustwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip -5pt 
\section{Education}
\parskip -5pt
% PhD Harvard
\datedsubsection{\textbf{Harvard T.H. Chan School of Public Health}}{05/2024}
\parskip -4pt \noindent Doctor of Philosophy (PhD) in Population Health Science, Public Health Nutrition \\
\textbf{Thesis: Policy, Systems, and Environmental Levers to Improve Diet, Population Health, and Health Equity in the US}\\

\vspace{-1em}


% SM Harvard
\datedsubsection{\textbf{Harvard T.H. Chan School of Public Health}}{05/2024}
\parskip -4pt \noindent Master of Science (SM) in Biostatistics

% Berkeley MS
\datedsubsection{\textbf{University of California, Berkeley School of Public Health}}{05/2019}
\parskip -4pt Master of Science (MS) in Epidemiology \\
    \vspace{-1em}
    \begingroup
    \addtolength{\leftmargini}{3em} \begin{itemize}
        \item[\hspace{1em}Thesis:] \text{\textit{Sugar-Sweetened Beverage Consumption 3 Years After the Berkeley, California, Sugar-Sweetened Beverage Tax}}
    \end{itemize}
    \endgroup
\parskip -8pt  

% Berkeley BA
\datedsubsection{\textbf{University of California, Berkeley}}{05/2016}
\parskip -4pt \noindent  Bachelor of Arts (BA) in Public Health, \textsc{Minors:} Global Poverty, Music

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Appointments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip -5pt 
\section{Academic and Professional Appointments}
\parskip -5pt
% SBS postdoc Harvard
\datedsubsection{\textbf{Postdoctoral Research Fellow}}{08/05/2024 - present}
\parskip -4pt \noindent Harvard T.H. Chan School of Public Health, Department of Social and Behavioral Sciences \\
CVD Epidemiology Training Program in Behavior, the Environment and Global Health \\
Hours per week: 40 hours
\begin{itemize}
    \item Support analyses of county-level policies that were implemented during the COVID-19 pandemic and its impact on child nutrition outcomes, using nationally-representative data, as part of the Social Policies for Health Equity Research (SPHERE) Center. \parskip 1pt
    \item Examine the impact of cash assistance programs, including the Earned Income Tax Credit and the Child Tax Credit, on child nutrition and health. \parskip 1pt
    \item Assess the relationship between changes to the WIC program, including increases in the monthly cash value voucher allocation for fresh fruits and vegetables, on retention and benefit redemption, using Massachusetts state-wide administrative data \parskip 1pt
    \item Responsible for project conceptualization, data cleaning, management, and analysis, manuscript preparation, and submission to peer-reviewed scientific journals and conferences \parskip 3pt
\end{itemize}

% \vspace{-1em}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parskip -5pt 
\nocite{*}
\printbibliography[title=Publications]

\vspace{2em}

\textit{Ad Hoc Reviewer for: The American Journal of Public Health (AJPH), PLOS ONE, PLOS Medicine, The American Journal of Preventive Medicine (AJPM) FOCUS, AJPM, Pediatrics, BMC Public Health, Scientific Reports, Frontiers in Nutrition, Preventive Medicine Reports, Public Health, International Journal of Obesity, Journal of Nutritional Science}


\section{Presentations}
\begin{enumerate}[leftmargin = 2em]
    \item \textbf{Lee MM}, Poole MK, Chen JT, Gortmaker SL, Stephenson BK, Haines J, Chavarro J, Kenney EL.  Longitudinal Changes in Adherence to US Dietary Guidelines and Associations With Body Mass Index Among Adolescents in the Growing Up Today Study: A Change-in-Change Study.  \textit{American Society of Nutrition Annual Meeting}. (July 2024). 
    \item \parskip 1pt Chapman LE, Richardson SA, Rimm EB, Gortmaker SL, \textbf{Lee MM}, Cohen JFW. Examining Student Plate Waste Following a Conversion From Pre-packaged to Scratch-Cooked Lunches Prepared On-Site: A Longitudinal Cohort Study. \textit{American Society of Nutrition Annual Meeting}. (July 2024). 
    \item \parskip 1pt \textbf{Lee MM}, Kenney EL, Carlson K, Novick E, Portocarrero P, Rimm EB, Chen JT, Gortmaker SL, Stephenson BK, Liebman J. Impact of unconditional cash transfers on diet during the COVID-19 pandemic: A randomized lottery experiment. \textit{American Public Health Association Annual Meeting}. (Nov 2023). 
    \item \parskip 1pt \textbf{Lee MM}, Gibson LA, Hua SV, Lowery CM, Paul M, Roberto CA, Lawman HG, Bleich SN, Mitra N, Kenney EL. Changes in advertising and store stocking practices among small, independent beverage retailers following a sweetened beverage excise tax in Philadelphia: A difference-in-differences study. \textit{American Public Health Association Annual Meeting}. (Nov 2023).  
    \item \parskip 1pt Chapman L, Richardson S, Rimm EB, Gortmaker SL, \textbf{Lee MM}, Cohen J. Daily saturated fat and sodium content of school meals among a nationally representative sample of elementary schools in the United States. \textit{American Public Health Association Annual Meeting}. (Nov 2023). 
    \item \parskip 1pt \textbf{Lee MM}, Barrett J, Kenney EL, Gouck J, Cradock AL, Long MW, Ward ZJ, Rohrer B, Gortmaker SL. Impacts of a state-wide sugar-sweetened beverage excise tax in California: Projected benefits for population obesity and health equity. \textit{American Public Health Association Annual Meeting}. (2022).
    \item \parskip 1pt Kenney EL, \textbf{Lee MM}, Barrett J, Ward ZJ, Long MW, Cradock AL, Gortmaker SL. The cost-effectiveness and health equity impacts of improved nutrition standards in WIC, and the potential for maximizing WIC’s benefits for population health. \textit{American Public Health Association Annual Meeting}. (2022).
    \item \parskip 1pt Yuan H, Schillinger D, Ponce J, \textbf{Lee MM},  Falbe J, Daniels R, Madsen K. Implementation of 3 sugar-sweetened beverage taxes in California Bay Area. \textit{American Public Health Association Annual Meeting}. (2019).
\end{enumerate}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Honors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards \& Honors}

\textit{APHA Annual Conference Food and Nutrition Abstract Award} \hfill {2023}\\
\textit{GSAS Professional Development Fund Recipient} \hfill {2023}\\
\textit{Irene M. \& Fredrick J. Stare Nutrition Education Fund Awardee} \hfill {2022}\\
\textit{Berkowitz Fellowship in Public Health} \hfill {2021}\\
\textit{Certificate of Distinction in Teaching, Derek Bok Center for Teaching and Learning} \hfill {2021}\\
\textit{Certificate of Distinction in Teaching, Derek Bok Center for Teaching and Learning} \hfill {2020}\\
\textit{Simon, Arpi, and Marie Simonian Research Excellence in Nutrition Prize} \hfill {2020} \\
\textit{Prajna Chair's Scholarship in Public Health Nutrition} \hfill 2019 \\
\textit{Reshetko Family Scholarship} \hfill 2017

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work \& Research Experience}

% Kenney
\datedsubsection{\textbf{Research Assistant}}{06/01/2020 - 08/01/2024}
\textit{Harvard T.H. Chan School of Public Health, Department of Nutrition} \\
PI: Erica Kenney, ScD, MPH \\
Hours per week: 10 hours
\begin{itemize}
    \item Led and supported data analysis, code review, and manuscript development and editing for projects related to nutrition policies aimed at addressing childhood obesity, improving food access, and reducing food insecurity -- including evaluations of US nutrition assistance programs, of the Philadelphia, PA, sweetened beverage excise tax, of racial/ethnic disparities in food-related advertising to young children and their families, and of WIC benefits expansions during the COVID-19 pandemic.
\end{itemize}

% CHOICES
\datedsubsection{\textbf{Research Assistant}}{06/01/2020 - 08/01/2024}
\textit{Harvard T.H. Chan School of Public Health, Department of Social and Behavioral Sciences} \\
PI: Steve Gortmaker, PhD, The Childhood Obesity Intervention Cost-Effectiveness Study (CHOICES)\\
Hours per week: 10 hours
\begin{itemize}
    \item Supported microsimulation-based cost-effectiveness analyses related to US policy interventions and their potential long-run impacts on child and adult outcomes, including health care spending, obesity, morbidity, and mortality. Analyzed dietary and health data from representative samples including the National Health and Nutrition Examination Survey, ran and synthesized output from simulation models, validated estimates against empirical data, and developed methods to streamline post-processing of results.
\end{itemize}

% UCB Madsen
\datedsubsection{\textbf{Graduate Researcher}}{08/01/2017 - 06/01/2019}
\textit{UC Berkeley School of Public Health Division of Community Health Sciences} \\
PI: Kristine Madsen, MD, MPH\\
Hours per week: 10 hours
\begin{itemize}
    \item Managed evaluation of sugar-sweetened beverage (SSB) taxes in Oakland, Berkeley, and San Francisco to assess the relationship between implementation and beverage consumption, using a quasi-experimental difference-in-differences design. Supported analysis for \textit{The Fit Study}, a three year cluster-randomized trial on the effects of BMI screening and reporting. Oversaw data collection, entry, analysis, and manuscript development and submission.
\end{itemize}

% UCB Mujahid/Bradshaw
\datedsubsection{\textbf{Staff Research Associate}}{06/01/2016 - 07/31/2017}
\textit{UC Berkeley School of Public Health Division of Epidemiology} \\
PI: Mahasin Mujahid, PhD, MS; Patrick Bradshaw, PhD, MS\\
Hours per week: 40 hours
\begin{itemize}
    \item Managed research portfolio, including background literature reviews, Institutional Review Board (IRB) and ethics approval and documentation, accounting and finance reporting, data management, manuscript preparation and submission, and grant proposals. Provided teaching support for undergraduate-level Epidemiologic Methods course.
\end{itemize}

% UCB Mujahid/Carly
\datedsubsection{\textbf{Research Assistant}}{08/01/2015 - 06/01/2016}
\textit{UC Berkeley School of Public Health Division of Epidemiology} \\
PI: Mahasin Mujahid, PhD, MS\\
Hours per week: 5 hours
\begin{itemize}
    \item Completed detailed literature review on the impact of community change initiatives on neighborhood collective efficacy. Coded, transcribed, and analyzed qualitative data using Atlas.ti.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEACHING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip -5pt 
\section{Teaching}

% PHS 2000A/B
\datedsubsection{\textbf{Teaching Fellow, Population Health Sciences 2000 A/B}}{Fall 2020, Spring 2021, Fall 2022}
``Quantitative Research Methods in Population Health Sciences'' | \textit{Harvard Graduate School of Arts and Sciences}\\
Hours per week: 10 hours
\begin{itemize}
  \vspace{0em} \item Year-long core course for first-year PhD students in the Population Health Sciences doctoral program, covering concepts in sampling, estimation and statistical inference for regression models, model selection, survival and longitudinal analyses, measurement error, causal inference and mediation, and econometrics. 
  \item \parskip 1pt Led lab sessions and weekly office hours with original lecture slides including applications using the R programming language, development and grading of homework and exam assessments, and primary role in course evaluation and refinement during transition to online/virtual learning. Lab lectures given included material on regression, measurement error, survival analysis, causal interaction and mediation, factor analysis, and meta-analysis.
\end{itemize}

% SBS 203/204
\datedsubsection{\textbf{Teaching Fellow, Social and Behavioral Sciences 203/204}}{Spring 2022, Spring 2023, Spring 2024}
``Program Implementation and Evaluation'' | \textit{Harvard T.H. Chan School of Public Health}\\
Hours per week: 10 hours
\begin{itemize}
  \vspace{0em} \item Semester course on conducting community health needs assessment, program planning, implementation, and evaluation, with a particular emphasis on community engagement and applied research. Required for masters students in Social and Behavioral Sciences. Foci includes health-related intervention for individuals, communities, organizations, and local/national groups and the various challenges that researchers and practitioners encounter when conducting this work "on the ground". 
  \item \parskip 1pt Facilitated in-class discussion on theoretical concepts and course materials, led lecture in cost effectiveness analysis and economic evaluation in the context of program planning, and provided critical feedback on student work, including a community health needs assessment and CDC \textit{Partnerships for Improving Community Health} grant application among others. 
\end{itemize}

% NUT 202
\datedsubsection{\textbf{Teaching Fellow, Nutrition 202}}{Spring 2022}
``The Biological Basis of Human Nutrition'' | \textit{Harvard T.H. Chan School of Public Health, Biological Sciences in Public Health}\\
Hours per week: 10 hours
\begin{itemize}
  \vspace{0em} \item Semester course on the biochemistry and metabolism of carbohydrates, fats, proteins, vitamins, and minerals in the context of human disease. Contemporary topics are emphasized. Particular emphasis is given to current knowledge of the mechanisms that may explain the role of diet in the causation and/or prevention of ischemic heart disease, diabetes, obesity, hypertension, and cancer. Required for masters and doctoral students in Nutrition.
  \item \parskip 1pt Coordinated weekly guest lectures and held weekly office hour review sessions on course material, led lecture in iron and copper metabolism in the context of human nutrition and health, drafted and evaluated exam questions and facilitated course feedback.
\end{itemize}

% PHS 2000A/B Tutor
\datedsubsection{\textbf{Tutor, Population Health Sciences 2000 A/B}}{Fall 2021, Spring 2022}
``Quantitative Research Methods in Population Health Sciences'' | \textit{Harvard Graduate School of Arts and Sciences}\\
Hours per week: 2 hours
\begin{itemize}
  \vspace{0em} \item Hosted weekly tutoring sessions for 2-3 first-year PhD students in Population Health Sciences to support learning in PHS 2000A and B (course description above), review concepts in preparation for exams, go over solutions and concepts from problem sets, and provide mentoring on additional classes and resources.
\end{itemize}





\end{document}